BugTracking: A tool to assist in the identification of bug reports

### 2016-01-15 OSS_2016/paper.tex
Adding some data and changing the title

\title*{BugTracking: A tool to assist in the Bug Triage Process}
% Use \titlerunning{Short Title} for an abbreviated version of
% your contribution title if the original one is too long
\author{Gema Rodriguez\inst{1}, Jesus M. Gonzalez-Barahona\inst{1} \and Gregorio Robles\inst{1}}
%\and Name of Author\inst{2}}
% Use \authorrunning{Short Title} for an abbreviated version of
% your contribution title if the original one is too long
\institute{\texttt{gerope@libresoft.es}, \texttt{jgb@gsyc.es},\texttt{grex@gsyc.es}
\and GSyC/LibreSoft, Universidad Rey Juan Carlos}
%
% Use the package "url.sty" to avoid
% problems with special characters
% used in your e-mail or web address
%
\maketitle

@@

\begin{table}[htb]
\begin{center} {\footnotesize
\caption{ Classification statistics of each developer}
\label{tab:1}
\begin{tabular}{lllll}
\toprule[0.3mm]%{\smallskip}
  & Bug Report\kern 1pc & Not Bug Report\kern 1pc & Undecided\kern 1pc & Total \\\hline
Developer 1 \kern 1pc & 53.89\% & 34.13\% & 11.98\% & 334 \\
Developer 2 \kern 1pc & --\% & --\% & --\% & 125\\
Developer 3 \kern 1pc & --\% & --\% & --\% & 125\\
\bottomrule[0.3mm]
\end{tabular} }
\end{center}
\end{table}

>>>>

\title*{BugTracking: A tool to assist in the identification of bug reports}
% Use \titlerunning{Short Title} for an abbreviated version of
% your contribution title if the original one is too long
\author{Gema Rodriguez\inst{1}, Jesus M. Gonzalez-Barahona\inst{1} \and Gregorio Robles\inst{1}}
%\and Name of Author\inst{2}}
% Use \authorrunning{Short Title} for an abbreviated version of
% your contribution title if the original one is too long
\institute{\texttt{gerope@libresoft.es}, \texttt{jgb@gsyc.es},\texttt{grex@gsyc.es}
\and GSyC/LibreSoft, Universidad Rey Juan Carlos}
%
% Use the package "url.sty" to avoid
% problems with special characters
% used in your e-mail or web address
%
\maketitle

@@

\begin{table}[htb]
\begin{center} {\footnotesize
\caption{ Classification statistics of each developer}
\label{tab:1}
\begin{tabular}{lllll}
\toprule[0.3mm]%{\smallskip}
  & Bug Report\kern 1pc & Not Bug Report\kern 1pc & Undecided\kern 1pc & Total \\\hline
Developer 1 \kern 1pc & (180)-54\% & (114)-34\% & (40)-12\% & 334 \\
Developer 2 \kern 1pc & (188)-76\% & (51)-21\% & (8)-3\% & 247\\
Developer 3 \kern 1pc & (125)-55\% & (80)-35\% & (23)-10\% & 228\\
\bottomrule[0.3mm]
\end{tabular} }
\end{center}
\end{table}
